In your mail, you receive a letter from King Varian Wrynn of Stormwind.

\start{The Legion Returns}

Along with the letter is a Stormwind Portal Stone, a powerful magical rune granted to heroes of the Alliance during dire times.

Using the portal stone, you end up in Stormwind's Mage Tower, where you make your way down to Stormwind Harbor.

The docks are teeming with people. Everywhere you look, you can see soldiers, healers, gryphon riders, gyrocopters... There are military tents near the entrance to the docks, soldiers practicing over target dummies, and supplies being shipped on boats. You have never seen an army like this one before.

The noise in the harbor is unprecedented, and you can make out some lines from here and there.

\miss{Recruiter Gearburns says: Don't give them any quarter!}

\miss{Recruiter Barker says: I cannot find your papers, citizen.}

Barker is currently taking the admissions of new Alliance Recruits. His colleague is waving at you.

\miss{Recruiter Lee says: I can help you over here, adventurer.}  % <name>

You approach the officer as he is standind by his desk.

\complete{The Legion Returns}

\start{To Be Prepared}

\miss{Recruiter Lee says: Stormwind appreciates your service!}

Walking through the harbor, you overhear a conversation between two officers.

\miss{Officer Blythe says: The third fleet has been deployed against the southern shores of the Broken Isles.}

\miss{Officer Carven says: No word has reached us from the front lines?}

You continue your way down the harbor as you pass by gyrocopters which are being checked before departure by gnomish engineers. As you reach the lower section, you hear a dwarf calling your way.

\miss{Gussof Forgefire says: Got some o' the forge's best armor polish for the troops here, adventurer. Don't be shipping off without gettin' some o' those scuffs out first.}  % <name>

Thanking the dward, you use the Keg of Armor Polish and polish your armor.

Look around you, you notice a draenei with strange crystals at the other side of the harbor. As you walk towards him, you continue to make out some conversations from around you.

\miss{Thurgrum Deepforge says: Delivery of cannons and cannonballs directly from the great forge for ye'.}

\miss{Clavicus Knavingham says: Excellent, the third fleet ships are loading up at the end of the dock.}

\miss{Alasdair Whitespeak says: Hurry up an' finish blessin' those bandages, we need to get them off to the front!}  % TODO: Blessed Bandages

As you near the Draenei crystal stand, he addresses you.

\miss{Voraatios the Benedictive says: We have brought crystals infused with the Light from the Exodar. Allow us a moment to enhance your weapon before you battle with the Legion.}

You hand your weapon to Voraatios as he uses the Light-Infused Crystals to empower it and give it back to you.

Thanking the enchanter and continuing to walk along the docks, you hear fighting noises and a crowd cheering coming from up the stairs. Returning to the higher level of the harbor, you notice soldiers and adventurers standing in a circle watching two people fight at its center, essentially creating a living duel ring. As you approach the ring, one of the officers addresses you.

\miss{Sergent Crowler says: The troops are itching for a fight, adventurer. Why don't you show them a few moves?}  % <name>

The battle in the ring over, one of the spectators addresses you.

% TODO: I don't know if the recruits says this, but other nps around do. I need to check it more throughly but I don't have any Alliance character at the right level anymore.
\miss{Alliance Recruit says: How about a duel? I could use a good fight.}

\miss{You say: Let's duel.}

You stand your ground in the ring and manage to defeat your opponent.

\miss{Alliance Recruit says: You have won.}

As the crowd is applauding, you salute then go back down the stairs to the lower section of the harbor. A Pandaren is inviting you to sit on a grand table with multiple dishes served.

\miss{Len-Shu says: Sit, friend, and enjoy this meal. You cannot fight on an empty stomach.}

Realizing the Pandaren is right, you sit at the table with other Alliance Recruits and start eating what may possibly be your last meal. You overhear some conversation from a mother and her children along the docks.

\miss{Ella says: Momma, is daddy coming home soon?}

\miss{Alaina Hearthsong says: Yes, baby, he'll be home before you know it.}

\miss{Sam says: I'll proctect you, Ella! I've got a sword and everything!}

\miss{Alaina Hearthsong says: Sam! Where did you get that stick? Put it down, it's dirty.}

Your meal eaten, you stand up and walk away from the table in direction of the docks, where you can make out some traders calls for customers along the way.

\miss{Rebecca Laughlin says: Tabards for sale! Show your colors on the front!}

\miss{Lenny "Fingers" McCoy says: Psst, hey, got some lucky charms here. Don't want to face the Legion without a little luck on your side, do ya?}

You continue your way towards the docks.

\miss{Recruiter Burns says: Your ship is waiting at the end of this dock, adventurer. Be careful out there.}  % <name>

Nodding to the recruiter, you continue walking on the docks towards the ship, where some soldiers recognize you and cheer.

\miss{Stormwind Honor Guard says: For the Alliance!}

\miss{Commander Sharp says: Give them hell, adventurer.}  % name

You reach the end of the docks and are impressed by the number of ships that have already taken sails from the harbor to the Broken Isles. The Alliance is truly giving everything to deny the Legion a foothold on this world before it's too late to stop it.

Waving at you, a knight addresses you.

\miss{Knight Dameron says: This is your ship, adventurer. Light be with you.}  % <name>

Noticing your polished armor and empowered weapon, he continues on.

\complete{To Be Prepared}

He hands you a Signet of Stormwind, one of the rings granted to heroes of the Alliance shipping out to the battle of the Broken Shore.  % TODO: add \desc

\start{The Battle for Broken Shore}

Thanking Knight Dameron, you board the ship as you are greated by a stout dwarf rogue near the mast.

\miss{Lorcan Flintedge says: Aye, another mission where we might not be makin' it back. Brought me private stash this time, though. Ye want a sip?}

\ask{Drink from Lorcan's private stash ?}
\goto[Yes]{?}
\miss{You say: Sure, I'll take a sip.}
Lorcan hands you his flask and you take a sip from it. It is so strong that you instantly feel drunk. Woah! Accepting a drink from a seasonned dwarf rogue who considers this might be his very last since he might die in the next few hours probably wasn't a great idea. % TODO: notice the bucket and use it

\goto[No]{?}
You realize that accepting a drink from a seasonned dwarf rogue who considers this might be his very last one since he might die in the next few hours is probably a bad idea.
\miss{You say: No, thank you.}

You walk towards Captain Angelica, as she is the one in charge abord the ship.

\miss{Captain Angelica says: Welcome aboard, adventurer. We're all stocked and ready to ship out just as soon as you're ready.}

\miss{You say: I am ready to face the Legion.}

Your ship takes sails from the docks and is quickly joined by other ships departing as well. The sky around the fleet is gradually filled with gryphon riders and gyrocopters as you pass by Stormwind's lighthouse and sail to the Broken Shore.

% TODO: scenario

% TODO: doomsayers ? <- invasions after the assault
