\textit{Across the breadth of Azeroth, the Horde and the Alliance have dealt crushing blows to Deathwing's elemental minions and fanatic Twilight's Hammer cultists. Through it all, the Earthen Ring has never wavered from its tireless charge, holding Azeroth itself together amid the tidal fury and errant magical energies that churn at the Maelstrom. Yet as the elements continue their chaotic upheaval, it seems that the noble shamanic order might finally be on the verge of breaking beneath the great weight that rests on its shoulders. Even Thrall, for all of his wisdom and skill, has grown aggravated by his failure to effectively communicate with Azeroth's elements. Recently, his calls were acknowledged, but the malevolent entity that responded has only intensified Thrall's fears and doubts....}

% Source: https://worldofwarcraft.com/en-us/news/2950664/patch-4-2-rage-of-the-firelands-trailer-revealed

\begin{center}
  $\ast$~$\ast$~$\ast$
\end{center}

Thrall stands over the great rift within the Maelstrom, channeling his energy into sealing it, when Aggra approaches.

Aggra says: You've been at this for days, Go'el.

Thrall says: The elements remain silent, Aggra. How can I help them if they won't speak to me?

Aggra says: You must rest. Everyone has their limits.

Thrall says: Look around you. This world is dying! I can't have limits.

Aggra says: When will you see... that you cannot carry this burden alone?

Aggra turns and walks away. Thrall is seen shortly after seated on the rock, communing with the elements.

Thrall says: Great spirits, please, speak to me! Show me what I must do.

The rift within the Maelstrom glows incredibly bright red, and a pillar of fire bursts from it. As Thrall stares in astonishment, Ragnaros rips through the rift!

Ragnaros says: YOU CALLED, LITTLE SHAMAN... AND THE FIRELORD HAS ANSWERED!

Ragnaros says: YOU AND YOUR KIND THOUGHT THAT THE FIRES OF DOOM HAD BEEN QUENCHED...

Ragnaros raises Thrall into the air with a pillar of fire.

Ragnaros says: BUT I WILL SHOW YOU THE TRUTH!

As Thrall hovers into the air, images of the Firelands flash through Thrall's mind. The images then change to a view of the forests of Mount Hyjal, surrounding the World Tree Nordrassil.

Ragnaros says: THIS WORLD AND ALL THAT YOU HOLD DEAR EXIST ONLY TO BURN!

Suddenly, Nordrassil is set ablaze, and a great wave of fire envelops Mount Hyjal and beyond, heading for the city of Orgrimmar as Thrall watches from nearby.

Ragnaros says: THE END COMES, SON OF DUROTAN... THE FINAL HOUR OF TWILIGHT.

The gates of Orgrimmar explode and crumble, as the wave of fire continues.

Ragnaros says: AND THERE IS NOTHING YOU CAN DO TO STOP IT!

Ragnaros laughs maniacally as the fire wave approaches Thrall.

Thrall says: NOOO!!!!!

Back in the Maelstrom, Thrall falls to his hands and knees, overcome by the vision.

Go'el! I heard you call out... what's happened?

Thrall says: Fire, Aggra... it's coming for us. Unstoppable, unending rage...

Aggra helps Thrall to his feet.

Aggra says: Take heart, Go'el. The end is not upon us yet.

Thrall smiles and touches Aggra's cheek, then holds her to him.

Thrall says: Whatever comes, I know we will face it... together.
