\says{38535}{38521}  % Why hello there, fellow member of the Alliance! As an official representative of Gadgetzan, I'm here to make sure we poor scattered gnomes can peacefully co-exist with the Steamwheedle goblins here in Gadgetzan! We may even be open to tolerating the presence of their new Horde goblin friends. I'm sure we can all come to an agreeable decision with your help!

\startID{25049}  % Puddle Stomping

\startID{25048}  % Seaside Salvage

On your way out of the town, a goblin addresses you.

\startID{25112}  % Butcherbot

You exit Gadgetzan towards the coast. You notice Bloodsail pirate ships at the far end of the bay, and some Sea Giants walking in the shallows south, their enormous feet crashing over some supplies crates half submerged by the sea. You enter the shallows and manage to kill a few of the giants. As you start recovering the Steamwheedle Supplies, you are attacked by a Southsea Scoundrel.

% TODO: Maybe recover more than one crate and be attacked by more than one pirate ? Currently, they seem more of a nuisance in the game than here.
\says{40665}{40573} \text{40574} \text{40575}  % That be property 'o the Southsea Freebooters now, landlubber! Ye'll not get around our blockade with scavengin'! The Southsea Freebooters own this shore!

Seems like Gadgetzan has a pirate problem. This one was probably afraid of the Sea Giants and was waiting in hiding for some brave soul to kill the giants for him so he would just need to loot the crates. That could have been a sound strategy, except someone able to take on the giants will have no problem handling with him.

You make short work of the pirate and, as you start heading back to Gadgetzan, you notice some Glasshide Basilisk in the nearby dunes. You kill a few of them then use the Buthcerbot Control Gizmo to \itemuse{52715}.  % deploy a Butcherbot to harvest parts from a slain animal.

\says{39696}{39703} \text{39700}  % Increase your profit potential with Butcherbot! No part goes to waste! Yay!

The small robot then starts clawing at the carcass and harvest meat from it, storing it inside a safe compartment of itself.

After you harvested enough of the Glasshide Basilisks, you head back to Gadgetzan, where Driz is waiting for you.

\completeID{25112}  % Butcherbot

\startID{25111}  % Scavengers Scavenged  TODO: when to do this ? If needed, I can put the Butcherbot quests in their own part. If I do that, I could even ask the reader if he wants to do it (it's really a butchering quest.) However, this chapter would be pretty dull. I'll need to see whether I can include these quests in the storyline quests of the zone or not.

Reassuring Driz about your abilities, you walk back towards Kelsey.

\completeID{25049}  % Puddle Stomping

\progressID{25048}  % Seaside Salvage

You show Kelsey the crates you salvaged from the Sea Giants.

\completeID{25048}  % Seaside Salvage

You are not sure why the goblins of Gadgetzan want to recover these supplies because, honestly, it \itemflavor{50829}.  % looks like a bunch of junk.

\says{38535}{40567}  % There you go, Mister Noggenfogger! You won't have to worry about those giants anymore!

\says{38532}{40568}  % That's actually a load off my plate. Thanks, kid.

\says{38534}{40569}  % Tch. Amateurs.

Kelsey turns back to face you.

\startID{25050}  % Rocket Rescue

You exit the walls of Gadgetzan through the north-eastern and find the \miss{Steamwheedle Rescue Balloon} waiting for you near the docks. As Kelsey arrives holding some rockets, you both step inside the balloon and lift off.

You fly by the pirate blockade and reach a small set of islands and debris near the sea. This is the previous location of Steamwheedle Port, before the Cataclysm changed the coastline of Tanaris. The refugees are desperately trying to survive on the small islands and on the debris of some buildings.

You lob some Life Rocket pack out of the cannon and deliver them to the Steamwheedle survivors. When the pack reaches the land, the goblins scurry about it, as they strap the Life Rocket on their back and fire it up to fly back to the safety of Gadgetzan.

Kelsey then drives the balloon back to the town, accross the Southsea pirates blockade. As you pass near the ships, you use the balloon's cannons to \miss{throw large bombs to blow up any Southsea Blockaders near the point of impact}. After a while and some dead blockaders, the pirates notice the damage you wrought and start firing their cannons at your balloon. It quickly becomes unstable as a result of the attacks, and Kelsey decides it is time to use the \miss{Emergency Rocket Pack} so that you can both safely \miss{return to Gadgetzan} before you are shot down by the pirates. Both of you strap an emergency rocket to your back and light it up, exiting the basket right before the balloon explodes in midair.

Of course, this being goblin engineering, the \miss{Emergency Rocket-Pack}'s engine starts to fail while nearing the walls of Gadgetzan. Fearing the rocket would explode while on flight, you unstrap it from your back as you barely survive the fall thanks to the sands of Tanaris. You make your way back in town when you see Kelsey running towards you from where Marin and Megs were standing.

% The description of Rocket Rescue says that Marin asked us to take care of the remaining pirates. However, nothing happens in game to reflect this, Marin just stays there, playing his dialogue about the two girls driving him insane. Because of this, I need to move Kelsey away from Marin when she gives you the quest, so that this discussion can have happened right before she reaches you.
\completeID{25050}  % Rocket Rescue

She hands you a gold coin and a purse full of silvers.

\startID{25121}  % Momentum
