\subzone{Ban'ethil Barrow Den}

% TODO: make it clearer that the druids have been kidnapped, not killed

Without losing any more time, you enter Ban'ethil Barrow Den. The entrance of the den spirals underground, with some lanterns hanging from the roof along the way. At the end of the spiraling path, you find the way guarded by Gnarlpine furbolgs. The path is still going down, even if it is not spiraling anymore. Fighting your way through it, you reach a room of the den with a high ceiling, where the path splits in three ways. The left one goes farther down, while the center and right ones have bridges that closes the gaps created by the lower reaches of the den. Before you could choose a way to go, you hear the footsteps of someone running in your direction from behind you.

% TODO: Explain that there is some light in the cave !

% TODO: Dammit, I forgot it was said the sentinel was already there before you !
% TODO: I need to d/c with Elannah to check the other sentences that she says like "take the scenic route" and try to amalgam them as much as possible.
\miss{Sentinel Huntress says: Kyra said you might need some help.} % TODO: add to wowpedia

Glad to have a bit of company in these caves, you greet the Sentinel Huntress and start on with the path to the right. You reach a chamber where an anguished Night Elf spirit seeks your help.

\start{The Sleeping Drud}

Realizing the only fay forward is actually backward, you return to the center of the chamber and set out to find the furbolg charm alongside the four relics.

You try the path to the center, which leads to a door which appears to be locked. You can hear angered cries and growls from the other side of the door. Clearly what is inside would rather be outside.

\miss{Sentinel Huntress says: Need some help finding your way? I know this place like the back of my hand.}

\miss{You say: Where is the Rune of Nesting ?}

\miss{Sentinel Huntress whispers: The Rune of Nesting is located accross the bridge in the upper section of the southern chamber.}

Walking back to the center of the room, the Sentinel crouches on the floor, and pours some kind of blue-green volatile powder out of her pouch, which quikcly forms a small cloud hovering on the ground.

\miss{Sentinel Huntress whispers: The mist will lead the way.}

The cloud then hovers in the left path, turning right under the bridges of the two other ways. You realize that if the "upper" section is below your current location, then the "lower" section must be even further down into the ground, implying that the depth of the den is daunting to say the least.

You start running behind the mist, when you are attacked by furblogs. Fighting your way through the tunnels, you reach another room with a high ceiling. The cloud continues forward, crossing a bridge, then disappears into the ground. At the end of the bridge is a small empty room, safe from some bones lithering up the floor and a chest. You open the chest and take the Rune of Nesting from it. So this must be the southern chamber.

\miss{Sentinel Huntress says: I haven't seen any of the sleeping druids. They must have been taken from here already.}

Fearing that the bones were actually the missing druids, you decide to just ignore the thought and continue your search.

\miss{You say: Where is the Black Feather Quill ?}

\miss{Sentinel Huntress whispers: The Black Feather Quill is located down the ramp in the lower section of the southern chamber.}

You turn back and then right, taking the path that turns further right so that you go under the bridge you just crossed. The ramp goes down and down until you reach a chamber in which lies a big furbolg with blue fur. This is unusual as the other furbolgs had brown or white fur. Unfortunately, you don't have time to ponder why this particular furbolg is different as he attacks you as soon as you approach the chamber. Fortunately, he is no match for you and the Sentinel. Behind his corpse, you notice a small chest. Opening it, you find the Black Feather Quill.

\miss{Sentinel Huntress says: It saddens me to see the furblog all corrupted so readily. These used to be our friends.}
\miss{Sentinel Huntress says: There has to be a way to stop this corruption before it consumes us all.}
\miss{Sentinel Huntress says: This place is infested... we'll need to make our way out of here with the relics as quickly as possible.}

\miss{You say: Where is the Sapphire of Sky ?}

\miss{Sentinel Huntress whispers: The Sapphire of Sky is located at the seperate room in the lower section of the northern chamber.}

She again crouches on the floor and a new hovering cloud of mist materializes soon after. Following the cloud, you run up the ramp then continues forward to the north. The path goes down again it starts to look as if this den has no end at all. There are many furbolgs in the tunnels, and fighting your way in such close environment is exhausting.

You end up in a big room with a central platform and paths that lead up to the top of the platform and even higher in the chamber. You figure this must be the northern chamber. The hovering cloud circles around the platform and enters a small room in the lowest reaches of the den before dissipating. You enter the small room and finds a chest partially buried in dirt and bones. You open the chest and find the Sapphire of the Sky.

\miss{Sentinel Huntress says: Damn you, Fandral! What have you gotten us into with this cursed "World Tree?"}

The tone of her voice betraying her anguish, you wonder if the Sentinel finally realized the bones could be the druids. Thinking that, after all, they could also be furbolg bones, you choose to focus on the task at hand.

\miss{You say: Where is the Raven Claw Talisman ?}

\miss{Sentinel Huntress whispers: The Raven Claw Talisman is located on the ledge in the upper section of the northern chamber.}

Realizing the relic is higher in the chamber, you ascend to the platform before the Sentinel had time to create a new mist cloud. From the platform, you can see a chest sitting on a balcony high in front of you. Two bridges going higher are starting from the platform, but fortunately the Sentinel knows which one leads to the balcony. She starts running on the bridge to the right, when she is attacked by more furbolgs. You follow her and fight your way up the balcony together. Reaching the chest, you open it and take the Raven Claw Talisman.

\miss{Sentinel Huntress says: We should have seen this coming. The corruption has been spreading for quite some time.}
\miss{Sentinel Huntress says: If the furbolg could be this far gone, what does that say for the rest of Teldrassil ?}

While the Sentinel tone seems more and more depressive, you realize that this entire area is completely devoid of any bone, regardless of their origin. Your heart light up with the realization that you did not find a single corpse at all throughout the den, meaning hope is not lost for the missing druids. The four relics found, you set out to return to the spirit you encountered earlier in the den.

\miss{You say: Where is Oben Rageclaw ?}

\miss{Sentinel Huntress says: Oben Rageclaw resides at the double bridges in the western chamber, near the hallway that leads out of the Barrow Den.}

A new cloud of mist soon appears besides the crouching Sentinel. The mists exits the balcony to the platform then takes the second bridge. You are relieved to realize the den is somewhat circular and you won't have to retrace your steps back.

Following the cloud, you take the path going up to the first chamber then cross the bridge to return to the room where the spirit of Oben Rageclaw awaits you.

%\miss{Sentinel Huntress says: Sometimes the mist cannot find its way if we are too far. Let's venture further and try again.}

\progress{The Sleeping Druid}

You show the spirit the Shaman Voodoo Charm you found on the furbolg.

\complete{The Sleeping Druid}

\start{Druid of the Claw}
\progress*{Druid of the Claw}

Realizing he is talking about the locked door you saw earlier in the den, you turn back to the bridge leading to the door. As you cross the bridge, the door slams open and you discover Rageclaw's body controlled by a furbolg shaman. Rageclaw transforms into a bear and charges at you while the Sentinel engages the shaman. % TODO: the fight

\complete{Druid of the Claw}

The spirit of Oben points to a small heap of earth. Rummaging through it, you find a chest with a few silver coins in it. Putting them in your bag, you turn to the Sentinel.

\miss{You say: Can you lead me to the exit ?}

\miss{Sentinel Huntress says: The exit is to the northwest... the mist will lead the way.}

Following the mist for the last time, you follow the ramp up from the first chamber into the spiraling path upwards and you manage to exit the Ban'ethil Barrow Den.

You start running to the east in direction of Dolanaar to bring back the Relics of Wakening.
