\subzone{Return to Dolanaar}

You return to Athridas and his Sentinels in the inn. As you approach him holding the relics, he addresses you.

\complete{The Relics of Wakening}

\complete{Resident Danger}

\start{Ursal the Mauler}

You are back on the road to the northwest. Along the road is a small pathway that leads higher in the woods into The Cleft. At the crossroads are a moon priestess and two sentinels who seem to be guarding her. One of them is looking at the road from atop her nightsaber while the other is in a fighting pose, looking at a furbolg up the hill in case he would try to descend upon them.

% TODO: can be attacked by either a gnarlpine defender or a nightsaber near the crossroads and rescued by the sentinels and the moon priestess, because they engage mobs near them

\start{The Road to Darnassus}

Letting the immediate defense of the road to the three of them, you take the path north into furbolg territory, and start your incursion into The Cleft by killing the furbolg that was menacingly close to the road.

The path is narrow and goes up into the hills, with a ravine on the left. It turns right and goes even higher into the highest reaches of the forest.

% Black furbolg guarding the small cave of Ursal. "Grimmaw"
% Ursal is in a small "boss cave", inside the case behind Ursal are multiple "Enslaved Druids of the Talon", they are sleeping and none of the fighting around them seems to rouse them.
% When Ursal is dead, the druids wake up. "Freed Druid of the Talon says: The nightmare of Ursal is over! We are free!" They transform into birds (such is how it is with ones of their callings) and escape the cave.

You return back to Amara.

\complete{The Road to Darnassus}

You make your way back to Dolanaar to let Athridas know that his ritual to awaken the Druids of the Talon has worked properly and that they are now freed from the furbolgs.

\complete{Ursal the Mauler}

% TODO: Syral Bladeleaf "Denalan's Earth"
