\textit{After years of imprisonment within the Emerald Nightmare, Archdruid Malfurion Stormrage has finally returned to the mortal world. Reunited with his love, Tyrande Whisperwind, Malfurion endeavors now to heal the corrupted world tree, Teldrassil, and rejuvenate the spirit of the night elf people. Yet, as the Great Cataclysm shakes the boughs of their colossal tree, the night elves brace themselves against the coming storm. As war and destruction close in from all sides, it falls to night elves like you to stand strong and protect the enduring legacy of your people.}

You start your journey at the top of Teldrassil, the world tree that is home to the night elves. The tree itself is so huge that it houses entire towns, lakes and woods. All around you are the verdant trees of Shadowglen, colorful in shades of green, purple and yellow. The wood is bathed in a quiet dusk, and dominated by the great tree Aldrassil which lies at the center of the clearing. There is a building at the base of the tree and a ramp going up around the trunk to reach the chambers in the higher branches. In front of you is Ilthalaine, the trainer of new Night Elves recruits.

\quotes{Ilthalaine}

\quest{The Balance of Nature}

Eager to prove your worth to Ilthalaine, you venture into the woods and start culling the population of young Nightsabers, the large saber cats that the Night Elves use as mount. It is a grim task, but keeping the balance of nature is primordial to Teldrassil. After having killed a few of them, you return to Ilthalaine, who is talking with two huntresses on the back of large Nightsabers.

\custom[Quest]{The Balance of Nature}{Notes}

The huntresses gone, Ilthalaine turns to you.

\complete{The Balance of Nature}

\quest{Fel Moss Corruption} \progress*{Fel Moss Corruption}

% Note: Normally, this quest is only offered after completing Fel Moss Corruption and it is not available if the player is already on Melithar's quest. Basically, this quest is intended to show new players that they were supposed to talk to Melithar as he had an exclamation mark on his head in case they missed it. In my case however, it does not make sense for me to make the adventurer go twice in the grells camp. I could simply ignore the quest, but I think it is better used to give the adventurer a reason to walk towards Melithar in the first place, even though the quest shouldn't be available yet.
\quest{A Favor for Melithar}

Nodding to Ilthalaine, you look into Melithar's direction. He is talking to a female Night Elf. He seems to be angry at something, while the female is calmly sitting on a bench. You walk towards them, overhearing the discussion.

\quotes[Quote]{Dirania Silvershine}

Noticing your approach, the male turns to you.

\complete{A Favor for Melithar}

Barely containing his rage, Melithar continues on.

\quest{Demonic Thieves}

Resolute that the grells are a nuisance to Shadowglen and Teldrassil as a whole, you venture farther into the woods again, past the Nightsabers area.

You see the grells dwellings, crude camps where these imp-like demons likely store the food that Melithar want you to recover. The grells are numerous but fearful, and they often prefer fleeing rather than helping their comrades as you attack them. Advancing through their territory, you manage to reach their camp where you find the missing food supplies. Inspecting their bodies on your way out of the camp, you find the moss that Ilthalaine wants to examine.

Back near the benches, you approach Melithar.

\progress{Demonic Thieves}

You give him the food supplies you recovered in the grell camp.

\complete{Demonic Thieves}

Thanking Melithar, you turn back to Ilthalaine, handing him the moss.

\complete{Fel Moss Corruption}

\start{Priestess of the Moon}

Waving goodbye to Ilthalaine, Melithar and Dirania, you circle around Andrassil and reach the two pools. Between the pools is a female Night Elf and her nightsaber mount. She is crouching besides a lying male. This is probably the Priestess of the Moon that Ilthalaine spoke about.

\complete{Priestess of the Moon}

\start{Iverron's Antidote}

Eying the ground all around the pools, you notice huge lillies with white petals, red stamen and an orange pistil. You gather some of them and bring them back to Dentaria.

\progress{Iverron's Antidote}

You hand the lillies to Dentaria.

\complete{Iverron's Antidote}

Dentaria uses the lillies and some nature magic on Iverron.

\custom[Quest]{Iverron's Antidote}{Notes}

\start{The Woodland Protector}

You go to the northern end of Shadowglen, where you find the Shadowthread cave. Nearing the entrance of the cave, you venture a glimpse inside it and see that it is covered in spider webs. You suddenly notice a dryad which appeared not to be there a moment ago. She vaguely resemble a female night elf for the upper part of her body, while the lower part is more akin to a woodland fawn.

\miss{Tarindrella says: You've come to help, adventurer? Let us stay together for a while.}

\complete{The Woodland Protector}

\start{Webwood Corruption}

You enter the cave with Tarindrella. The cave is dark and the Webwood Spiders are numerous, but you are not alone, as Tarindrella summons lashers to help you, that she calls Nature's Bite. Advancing through the cave, the webs grow thicker and the foulness of the air is worse and worse. % TODO: Describe the spiders

% TODO: Tarindrella tells us to seek Athridas !
\miss{Tarindrella says: Corruption this deep could not have come from the outside.}

You venture yet further into the cave. Some of Tarindrella's lashers are being torn apart regularly by spiders but she keeps summoning more of them as needed.

\miss{Tarindrella says: My dear friends... I'm so sorry...}

Unsure whether Tarindrella is sorry for killing the spiders or for sending her Nature's Bite lashers against them, you continue to advance in the cave.

\miss{Tarindrella says: The corruption goes much further than these spiders. I fear the true source is not within this cave.}

\complete{Webwood Corruption}

\start{Vile Touch}

You venture even further into the cave and you spot a spider that is five times larger than the other ones, this must be the broodmother. As Tarindrella summons new lashers, Githyiss the Vile start to attack you.

\miss{Tarindrella says: The corruption is buried deep within her.}

After the beast is killed, you notice a small totem behind the broodmother's corpse.

\miss{Tarindrella says: This totem has been corrupting the eggs ! It seems a greater threat looms. The Gnarlpine remain tainted by something most foul.}

\complete{Vile Touch}

Tarindrella smashes the totem with her hooves.

\start{Signs of Things to Come}

You close your eyes and, in the blink of an eye, you are back between the pools behind Aldrassil, besides Dentaria the Priestess of the Moon, and Iverron who is now standing and looking well. Iverron turns to you.

\quotes{Iverron}  % TODO: there is a bug, see Iverron's page history, and it still doesn't work.

Iverron says: I hear I have you to thank for helping to cure me. Thank you. Truly.

\complete{Signs of Things to Comee}

\start{Teldrassil: Crown of Azeroth}

Circling around the pool and passing behind Aldrassil, you continue northeast until you reach the moonwell. There are deers, nightsabers and boars, and you spot some lonely grells hiding in the leaves. Inside the moonwell, you think you can see a figure, like a spirit starting to appear from the water...

% TODO: There are two events here in the notes, I need a way to target only one of them !
\custom[Quest]{Teldrassil: Crown of Azeroth}{Notes}

Startled, you fill the Crytal Phial that Dentaria gave you with the waters of the well, and proceed to get back to her.

\progress{Teldrassil: Crown of Azeroth}

\complete*{Teldrassil: Crown of Azeroth}

\start{Precious Waters}

Looking towards Aldrassil, Dentaria points to the ramp.

% TODO: again, different Notes here
\custom[Quest]{Precious Waters}{Notes}

You thank her for her help and begin the ascencion of Aldrassil using the ramp around it. Tenaron's house is actually inside the tree, up in its branches. As you ascend the tree, you catch glimpses of conversations of some Night Elves who also live in Aldrassil.

\custom{Doranel Amberleaf}{Conversation}

Continuing your ascencion, you pass by a Shadowglen Sentinel who doesn't seem to notice you, instead continuing her duties. You finally reach the end of the ramp and Teranon's house. He notices you as you enter the alcove.

\custom[Quest]{Precious Waters}{Notes}  % TODO: target second note

\progress{Precious Waters}

\complete{Precious Waters}

\start{Teldrassil: Passing Awareness}

\miss{Tenaron Stormgrip says: Take with you the blessing of the wind's embrace. May it make your descent from Aldrassil more... direct.}

You feel the Wind's Embrace upon your body. You feel light as a feather and understand that Tenaron used his power over nature to grant you a slow fall from Aldrassil so you could reach Dolanaar quicker than by using the ramp down. You say goodbye to Tenaron and exit his house. Using a few metters of the ramp to gather momentum, you jump off the fence of the ramp and slowly, quitely, fall towards the roof of the building at the base of Aldrassil. While you fall, you can spot wisps in the trees, spirits of deceased night elves who have become one with the forest. Jumping off the roof, you land safely on the ground, where you start heading south east to exit Shadowglen.

You follow the paved road marked by small trees which branches form a bowl and look like they are hosting wisps. These natural lampposts illuminate the roads in the twilight of Shadowglen and the rest of Teldrassil.

% TODO: describe the arch as I'm using it later on to compare with Darnassus
The exit of Shadowglen is marked by a Night Elven arch, DESCRIPTION and guarded by Shadowglen Sentinels. Near the arch is a merchant, who waves to you.

\start{Dolanaar Delivery}

Since you were heading there anyway, you agree to help the merchant. You follow the road south until it goes east then reach a crossroads. You read the "panneau" and, since Dolanaar is "pointed" east, you continue the road to the east. If Shadowglen was a wood, the rest of Teldrassil is a forest. Trees of all sizes and colors dot the landscape. The only things that do not look natural here are some buildings in the south, and a strange creature along the road. It is humanoid in form, has light brown fur covering most of his body, big black hooves for feet and two giant horns pointing backwards. Curious, you step closer to him and, has he notices you and turn to face you, you notice he has the characteristic long ears of the elves and a face that, were it not for the fur and horns, could pass for a Night Elf.

\start{Zenn's Bidding}

\ask{Do Zenn's Bidding ?}
\goto{Zenn's Bidding}

Not trusting the satyr and refusing to kill animals for some strange rituals, you continue to follow the road to Dolanaar, as buildings start to appear from between the trees in front of you.

\goto{Dolanaar}
