After a good night sleep and on your way out of the inn, you notice a Night Elf clad in heavy armor. He has multiple Teldrassil Sentinels around him. He looks to be in charge here, and waiting for you. As you pass by him, he addresses you with a solemn tone.

\start{A Troubling Breeze}

You are startled by the directness of the request, but accept to check on the Great Warden, since you were heading east anyway.

The furbolg camp of Ferocitas the Dream Eater is directly besides Starbreeze Village to its north. You fight your way inside furbolg territory until you notice a blue-furred furbolg. Considering all other furbolgs have brown or white fur, and that this particular one has a green neckless on top of that, you quikcly understand that this must be their leader, Ferocitas.

You attack him as his mystics and warriors defenders come to his help. Furbolgs are not brave creatures, and they start to flee once you have injured them enough. As you kill Ferocitas, you take the green jewel hanging from his necklace.

Escaping the remaining furbolgs of the camp, you enter Starbreeze Village again, this time in search for Gaerolas. Since you did not cross him when you were looking for the Emerald Dreamcatcher, you start searching the other side of the village.

\rare{Uruson}
Around one of the buildings, you spot a blue-furred furbolg. Surely this is the leader of the furbolgs that have been invading Starbreeze Village. You quickly dispatch of the beast, and enter a building on your right as you are attacked by other furbolgs. % TODO: This is bad. There must be other furbolgs in the village before we encounter the other blue one

Nothing of note is on the first floor, except two furbolgs who attack you on sight. You are not sure whether they saw that you killed the blue-furred one, but they clearly don't want you to linger here regardless. As you ascend the stairs to the second floor after having killed the feral bear-men, you find a night elf body lying on the floor. Leaning over him, you realize he is not dead but injured.

\complete{A Troubling Breeze}

\start{Gnarlpine Corruption}

Understanding the urgency of the situation, you run off as quickly as possible to Dolanaar in order to warn Athridas. Unfortunately for Gaerolas, you don't have time to drag him away, as that would slow the warning and leave the sleeping druids completely defenseless. Since you killed most of the furbolgs in the area, you hope he will be safe until the Sentinels can spare a rescue party for Starbreeze Village.

As you approach Dolanaar, you see Tallonkai expecting your return. Running towards him, you take out his jewel from your bag and hand it quickly to him. There is no time to wait.

\complete{Ferocitas the Dream Eater}

Not even bothering to reply to him, you run to the inn and to Athridas. He is standing by Sentinel Kyra Starsong, that you can only guess is probably the commander of the Sentinels here in Dolanaar.

\complete{Gnarlpine Corruption}

\start{Resident Danger}

\start{The Relics of Wakening}
\progress*{The Relics of Wakening}

% \progress{Resident Danger} % TODO: wowpedia page is listing "on-accept" text in the progress section

Turning around, you notice a Sentinel on a Nightsaber that is very probably Citarre. She stares expectantly at you as you approach her.

\dialogue{Citarre Mapleheart}

Handing you a nightsaber, Citarre helps you to mount on it. Once you are properly secured on the nightsaber, she instructs it to transport you to Ban'ethil Barrow Den as fast as possible then come back to her.

Obeying her mistress, the nightsaber storms off Dolanaar and starts running as fast as it can to the west. You cross the paths of furbolgs and spiders in the forest, but none of them are able to match the speed of the nightsaber, allowing you to reach your destination safely. Upon reaching the entrance of the den, you dismount from the nightsaber and pet it to thank him for his swiftness. Looking happy to have been of help, the nightsaber turns around and starts running back to his mistress. % TODO: "You are in front of the den entrance" make it ominous or something
