As you reach Corithas Moonrage, you hand him the Filled Amethyst Phial.

\complete{Teldrassil: The Burden of the Kaldorei}

\start{Teldrassil: The Coming Dawn}

As you make your way south between the hills, you witness more wildlife being prey to Nightsaber Stalkers. You hope Ilthalaine will be able to restore the balance of nature on Teldrassil while you seek the source of its corruption. Reaching the moonwell near the Pools of Arlithrien, a spirit scene comes to life.

\custom[Quest]{Teldrassil: The Coming Dawn}{Notes}

You fill the Tourmaline Phial with the waters of the moonwell then, looking around, you notice a dryad gazing your way from the pools. Approaching her, you recognize Tarindrella from Shadowglen.

\progress{Teldrassil: The Coming Dawn}

\complete{Teldrassil: The Coming Dawn}

\start{The Vengeance of Elune}

As Tarindrella harnesses the power of the waters from the moonwells, she casts a powerful spell on you. Imbued with the power Nature and Moonlight, you become an embodiment of the Vengeance of Elune, the goddess herself.

You make your way to the south, looking for the source of Teldrassil's corruption. On your way to Gnarlpine Hold, you spot Ancient Teldrassil Protectors that are being assaulted by Corrupted Servants satyrs and their Corrupted Minions grells. Jumping into the fray, the light of Elune strikes at your will as it sears the corrupted and heals the protectors.

Along the way, you notice that your presence, filled with the power of Elune, enhances Teldrassil's own defenses, as thorned lashers grow out of the grass and attack the corrupted all alike.

Those Allies of Nature are vastly outnumbered by the Corrupted Gnarlpine fulborgs however, as they are vicious in defending their territory. You would like to help the lashers but you know you would never be able to kill all the corrupted before they are overrun. Using you as her beacon, Elune herself suddenly enacts a strong gravitational pull on your opponents, displacing them at your feet. With the corrupted all in one place and the Allies of Nature out of the way, Elune then channels her power through you, summoning a flurry of stars from the sky, instantly killing demons and furbolgs alike.

At the center of Gnarlpine Hold, you can finally witness the source of all this corruption. A giant ancient now lies before you. It seems to be diseased as his bark is dark grey, nearly black, and he is engulfed in an ominous dark blue aura. The Bough of Corruption, sensing the power of Elune within you, rushes to attack you. As he is seared by the Moonlight of Elune, he summons more of his corrupted minions to defend him. Channelling all her fury through you, Elune summons another flurry of stars from the sky. His bark burning from the pain inflicted by Elune's power, the Bough of Corruption drops to the floor, dead.

You return to Tarindrella at the Pools of Arlithrien while the Moonlight of Elune continues to sear the few remaining corrupted creatures along the way. When you reach Tarindrella, she is already smiling as she can sense that the source of the corruption as been dealt with.

\complete{The Vengeance of Elune}

Your task fulfilled, you sense the power of Elune leaving your body. You feel normal again.

\start{The Waters of Teldrassil}

You make your way back to Corithas at the crossroads near Darnassus. He is surprised you handled Tarindrella's task so quickly.

\progress{The Waters of Teldrassil}

\complete{The Waters of Teldrassil}

On your way to Darnassus, you are impressed by the enormous stone arch at the entrance of the city. It dwarfs the one at the exit of Shadowglen. Besides it are ancient protectors and a glaive thrower to defend the city of any threat. Sentinels are guarding the path below the arch. As you pass by them, you marvel at the architecture of the city. It is made of white stone with vines running alongside them and as well as wooden houses. Darnassus is open to the sky, and the graceful bridges spanning the lake around which it is built set the buildings wide apart. The elegant bridges, beautiful groves, and leaf-covered pathways that dot the city’s landscape are testaments to the night elves’ reverence for nature.

Darnassus is home to night elves of all vocations, and the city has recently opened its doors to human refugees from Gilneas as well. Many of these embattled humans have contracted a strange curse that transforms them into feral wolf-beasts known as worgen. Although they’re usually reclusive, the night elves have allowed these outsiders into Darnassus because they know the perils of the Gilneans’ cursed state all too well: it was, in fact, a group of night elf druids that created Azeroth’s first worgen millennia ago. Despite the arrival of these new residents, Darnassus remains a symbol of the night elves’ rich culture and glorious history.

One of Darnassus’s most notable structures is the stunning Temple of the Moon, the center of worship for High Priestess Tyrande Whisperwind and her Sisters of Elune. This is exactly where you are going.

Entering the Temple of the Moon, you can sense the peace and harmony that the light of Elune is bringing to this place of worship. You walk past the moonwell inside the temple and make your way up the ramp. You find Tyrande besides Malfurion, overlooking the temple from the upper level.

\progress{Home of the Kaldorei}

Humbled, you hand Tyrande the Filled Vessel containing the waters from all the moonwells you have visited.

\complete{Home of the Kaldorei}

Behind you, a sentinel who overheard the conversation accosts you.
% TODO: correct all the "accosts" into "addresses"

\start{Breaking Waves of Change}

Unwilling to let your brethren die because of the Cataclysm, you exit the Temple of the Moon and make your way to the teleportation tree near the Flight Master. The roots of the tree protrude from the ground and its trunk only begins to form above your height. A vibrant purple glow engulfs the tree from starting from the portal below the trunk and inside the space created by the roots. Stepping into the portal, you are teleported to Rut'theran, at the feet of Teldrassil, under a tree identical to the one you stepped into back in Darnassus.

Rut'theran used to be a small patch of ground nestled between two of Teldrassil roots. Since the Cataclysm, however, it is now a small island near the world tree, as part of its roots were broken by the power of the Shattering of the world. From the borders of Rut'theran, you can see Teldrassil in all its glory. After all this time spent on the top of the world tree , it is hard to realize you are now standing outside of it.

As you walk around the island, you notice there are three docks, with different ships waiting for travelers. One of them is an Alliance ship which comes from Stormwind in the Eastern Kingdoms, another is a small Night Elf ship going to the Exodar, the Draenei capital, and the last one is the ship on which the Worgen arrived from Gilneas, the dock hastily built in one of the broken roots.

Ruins in the water indicate that there used to be another dock in Rut'theran, which got destroyed when it was torn from Teldrassil's shadow by the Cataclysm.

You make your way to Vesprystus, the flight master of Rut'theran, and explain to him that you are going to Lor'danel to help the refugees. Putting you on his finest hippogryph, he wishes you goodbye as the beast soars in the sky in direction of Lor'danel in Darkshore.
