You return to Athridas and his Sentinels in the inn. As you approach him holding the relics, he addresses you.

\complete{The Relics of Wakening}

\complete{Resident Danger}

\start{Ursal the Mauler}

You are back on the road to the northwest. Along the road is a small pathway that leads higher in the woods into The Cleft. At the crossroads are a moon priestess and two sentinels who seem to be guarding her. One of them is looking at the road from atop her nightsaber while the other has her glaive in hand, looking at the furbolg up the hill in case he would try to descend upon them.

% TODO: can be attacked by either a gnarlpine defender or a nightsaber near the crossroads and rescued by the sentinels and the moon priestess, because they engage mobs near them (or going back from The Cleft)
% TODO: This might be a good opportunity to integrate Agal and his Gnarpile Augurs and Defenders. Curse of Weakness (augur)
% Maybe like "the road is still not safe since I got attacked by furbolgs on my way here so let's do this! leroy !"" then flee from agal then have Amara shot him ? Problem is that I can't leave just after that, so it would be better if she shoot him before her quest, except I don't have time because I need to kill Ursal.

\start{The Road to Darnassus}

Letting the immediate defense of the road to the three of them, you take the path north into furbolg territory, and start your incursion into The Cleft by killing the furbolg that was menacingly close to the road.

The path is narrow and goes up into the hills, with a ravine on the left. It turns right and goes into the highest reaches of the forest. The path is riddled with brown-furred Gnarlpine Ambushers and your ascension is slow as you have to kill the furbolgs along the way. You fear you might not kill Ursal in time for Athridas to complete the ritual.

\rare{Grimmaw}
At the top of the hill, you notice the entrace of a cave, guarded by a black-furred furblog. This must be Ursal's lair. Engaging the guard, you spot Enslaved Druids of the Talon sleeping in the cave as Ursal is toying with them. The roar of the guard alarms the blue-furred leader, who runs from the back of his cave to attack you. You manage to kill the black-furred guard and dodge Ursal's attack just in time to take advantage of his momemtum and kill him. The druids, completely oblivious to the fight around them until now, suddenly wake up together. It seems you killed Ursal just in time for Athridas to complete the wakening ritual.

\miss{Freed Druid of the Talon says: The nightmare of Ursal is over! We are free!}

They shift into birds, as is their druidic callings, and escape the cave, flying into the high trees of the forest.

The urgency of saving the Druids of Ban'ethil finally over, you walk out of The Cleft and back to Amara along the road.

\complete{The Road to Darnassus}

Bowing to the moon priestess, you make your way back to Dolanaar to let Athridas know that his ritual to awaken the Druids of the Talon has worked properly and that they are now freed from the furbolgs.

\complete{Ursal the Mauler}

Your task accomplished, you decide to go for a walk near the lake south of Dolanaar.

% TODO: here I could put Nyoma's flight master quest to make the reader go through the Flight Master page, but I fear it might be too convoluted.
