As you walk away from Denalan's tent and are attacked by frenzied Timberlings, the Cleansed Timberling runs to your location and defend you from his maddened siblings. As you continue towards Dolanaar, the Cleansed Timberling follows you, apparently intent in protecting you. On your way to Wellspring Hovel, you stop by Dolanaar's moonwell as Corithas is waving at you. Eyeing your Timberling, Corithas harbors a stern face.

\start{Teldrassil: The Burden of the Kaldorei}

Relaxing a little bit, Corithas looks through you as he is lost in thoughts.

\progress{Teldrassil: The Burden of the Kaldorei}

Taking the road to the west in direction of Darnassus, you continue your way accross a bridge and to Wellspring Hovel. You notice a planter with a night elf beside it. This must be Rellian, the other herbalist. He is startled at first to see your Timberling, but quickly regains his composure.
% Note: I redacted Denalan's presence here because:
% 1. It does not make sense to ask us to give the seeds to Rellian if he was going there anyway
% 2. Later in the quests he says he rushed here, so I'll have him appear at that time instead.

\progress{Rellian Greenspyre}

You show Rellian the Timberling Seed that Denalan gave you.

\complete{Rellian Greenspyre}

\start{Mossy Tumors}

Accepting the task from Rellian, you follow the road then turns north at the crossroads, in direction of Wellspring Lake and the the Oracle Glade.

Along the way, you notice that the nightsabers are pressuring the wildlife of Teldrassil. No matter where you look, you can spot rabbits and dears fleeing from their predators. Some Elder Nightsabers are even bold enough to attack you on the way, but your Cleansed Timberling fends them off easily. Now that you have witnessed firsthand the dire state of Teldrassil's balance, you understand why Ilthalaine tasked you to kill young nightsabers back in Shadowglen.

Following the road, you find yourself facing a huge tree. Its base is shaped like an enormous bear, and the top of the trunk looks like a giant bird taking flight from the bear's back. Clearly, the Oracle Glade is a marvel to behold. From the distance, you can spot multiple night elves at the base of tree.

You decide to stop by the moonwell first. You fill the Amethyst vial with the waters of the moonwell as a spirit scene comes to life.

\miss{Teldrassil: The Burden of the Kaldori} event

Walking closer to the huge tree, you notice one of the night elves is a priestess who looks to be crying as you approach her.

\start{Tears of the Moon}

It seems the corruption of Teldrassin can be felt even in this most beautiful of places. Noticing your willingness to help and the toughness of your Timberling protector, the sentinel near the priestess comes to speak with you.

\start{The Enchanted Glade}
\progress{The Enchanted Glade}

Accepting both tasks, you venture beyond the tree and into the surrounding woods. As you look for the harpies nest, you find yourself facing a Strange Fronded Plant, probably four times your height, with enormous leaves hanging down and a strange violet aura. It reminds you of the one you found near Lake Al'Ameth, except this one is even bigger and looks healthier. It has multiple layers of leaves and vibrant colors.

\start{The Shimmering Frond}

You take the Shimmering Frond from the fruit, and venture deeper into the woods, where you are ambushed by a group of harpies.

\miss{Bloodfeather Fury says: You will be easy prey, adventurer.}  % <class>

The Cleansed Timberling immediately jumps into the fray and kill multiple harpies, but is gravely injured at the arm, as the harpies talons shred into the vines. Fighting for your life, you manage to kill most of the others but only slightly injure the last one. She starts to flee as she realizes she is the only one remaining. Fearing she might be going to warn her sisters, you follow her direction.

Two turns in the woods later, you can't seem to find any trace of her. You spot two giant green spiders a few yards away. They look just like the ones in Shadowglen, except way bigger. You realize the harpy fled in fear, not necessarily to warn her siblings, and she ended up crossing into Lady Sathrah's territory. Taking advantage of your surprise at the sight of the spiders, the harpy suddenly strikes down from the treetops.

\miss{Bloodfeather Wind Witch says: My talons will shred your puny body, Night Elf.}

You avoid the deadly strike a split second before she reaches you, making her hit the ground with the momentum. As she tries to get back to you, the Cleansed Timberling finishes her off with a mightly blow from his good arm.

You take her belt into your bag to show to the sentinel. As you start walking back to where you killed the other harpies to take their belts as well, you notice an enormous gray spider running in your direction. You figure this must be Lady Sathrah as she is even bigger than the others, and she clearly does not want anyone threading in her territory.

You manage to kill her as the Cleansed Timberling fends off her attacks as best as it can, and you carve out her Silvery Spinnerets. The act takes time though, and you notice the other spiders closing in on you. The Spinnerets in your bag, you turn back and start running for your life. You pass by the place where you killed the other harpies and continue to run. You notice the spiders stopped following you, as if they fear lingering in the sadistic birds territory.

Your flight didn't go unnoticed however, and Bloodfeather Harpies, Rogue and Sorceress start to appear from everywhere in the woods.

\miss{Bloodfeather Sorceress says: A fine trophy your head will make, Night Elf.}

This group is not simply trying to rout you out of their territory, as they seek revenge for their fallen kin. As you try to run away, the leader of the harpies suddenly appears from the treetops and let out a Deafening Screech.\rare{Fury Shelda} The Cleansed Timberling smashes at the harpies, over and over again, ignoring the talons shredding at its vegetal body. As you return to your senses and kill their leader, the remaining harpies flee back into the woods. The Cleansed Timberling has saved your life once more, but it cost it dearly, as its body is mutilated everywhere.

The battle over, you expect the forest to return to its usual silence while you take the belts of the falling harpies. However, your senses still in alert, you hear a low growl from the nearby trees. Following the sound, you find an injured sabercat in the woods. It is a miracle it is still alive considering how far you are currently in harpies territory.

\start{Mist}

You make your way back to the Oracle Glade and escort the sabercat back to safety.

\miss{Sentinel Arynia Coudsbreak says: Mist! I feared I would never see you again! Yes, I am well, do not worry for me. You must rest and recover your health.}

\miss{Mist growls in acknowledgement before straightening and making her way off into the forest.}

\miss{Sentinel Arynia Coudsbreak says: Mist... It was my fault! The witches caught me off guard... I should not have let them take you...}

\complete{Mist}

Smiling to the Sentinel, you show her the harpies belts.

\complete{The Enchanted Glade}

Now facing Priestess A'moora, she addresses you.

\progress{Tears of the Moon}

You hand her Lady Sathrah's Silvery Spinnerets.

\complete{Tears of the Moon}

As the priestess holds the Silvery Spinnerets of Lady Sathrah in her hands and let a tear run her cheek, you see a spirit form forming at the base of the tree. You recognize the form of the grey spider, though it is only her spirit. She looks calm and back in harmony with nature's balance. She turns around the tree then disappears into the woods. Maybe she will be reborn in the future as Elune blesses her, bur for now, the \miss{Spirit of Sathrah is once again at peace.}

You decide it is time to go to Wellspring Lake and harvest the Mossy Tumors of the corrupted timberlings for Rellian. You travel south-east and, before you can even reach the lake, you find yourself attacked by Timberling Mire Beasts and Timberling Tramplers on the bank of Wellspring River.

It seems your Timberling is able to sense the corruption of his brethren, as he mercilessly kills them while you harvest the Mossy Tumors on their corpses. Curious as to where Wellspring River may go, you decide to follow its course. Arriving at the end of the river, you can see the water cascading from the boughs of Teldrassil in a great waterfall far below. You can't see the end of the waterfall as the water ends up hidden in Teldrassil lower branches. Teldrassil is so gigantic that you nearly forgot you were actually walking on its top the whole time.

As it is standing next to you, you notice sap is flowing slowly from the Timberling's wounds. You would like to help him since he saved your life in the woods, but you don't know what to do. Figuring out an herbalist might know better, you exit The Oracle Glade to return to Rellian in Wellspring Hovel. As you approach him, he turns to you.

\progress{Mossy Tumors}

You hand Rellian the Mossy Tumors.

\complete{Mossy Tumors}

You notice a Night Elf running your way, you recognise it is Denalan, the herbalist of Lake Al'Ameth.

\start{Oakenscowl}

Resolute to help Denalan fighting the corruption of the Timberlings, you first show him the Shimmering Frond you found in The Oracle Glade before departing.

\progress{The Shimmering Frond}
\complete{The Shimmering Frond}

% Note: This is bugged on live, this only happens if you turn in the quest to Denalan in Lake Al'Ameth, not if you turn it in to Denalan in Wellspring Hovel. Since this discrepency does not make sense from a gameplay standpoint, I'm considering the quest chain is not bugged and continues properly from here.
Denalan hurries to Rellian's planter and plants the frond you gave him.

\miss{Denalan says: I hope this frond takes root...}

A moment later, you see the fronds growing before your very eyes, as three plants now fill the planter.

\complete{The Sprouted Fronds}

% Note: At the end of "The Sprouted Fronds", you get healing herbs. However, the herbalist npcs never say anything about it, so you only know these are healing herbs from the tooltip, which is not transposable here. Because of this, I decided to injure the Timberling in the woods so that it would be the one making the aventurer realize the healing properties of the fronds.
Unlike the expirement at Lake Al'Ameth, these ones actually grew uncorrupted. You manage to harvest multiple Sprouted Fronds from the plants in the planter. The Cleansed Timberling, probably sensing something in the fronds, takes one of them and rubs his arm with them. Before your very eyes, the vines of his arm reform themselves to close the wound. Amazed, you take more of the fronds and rub them on the remaining wounds, fully healing the Timberling. Happy to have returned the favour of saving the Cleansed Timberling, you decide to gift the remaining Sprouted Fronds to the herbalists so they can study their restorative properties further.

Eager to stop the Timberlings corruption, you make your way to Wellspring Lake and start looking for around Oakenscowl around the shore. After a few minutes of wandering about, you spot a huge Timberling which body appears to be red. As you get closer, you realize its body is formed from dissecated brown vines, and the red hue comes from the tumor itself which seems to have taken root in all parts of its body. The Cleansed Timberling rushes to attack it as you realize this is actually Oakenscowl. Joining the fray, you notice the Cleansed Timberling is battling with fervor and determination, caught in a frenzy the like you have never seen. After a hard-fought battle, the corpse of Oakenscowl finally drops to the floor, as you start carving the Gargantuan Tumor out of its body.

As you walk away from the dead Timberling body, you notice that the Cleansed Timberling has been standing by the lake since the end of the fight. You stay there for a few minutes when you realize it is not going to move at all. Just as it started to protect you with no apparent reason, it has now found a place to rest. The source of the Timberlings corruption finally destroyed, it looks to be at peace with nature, like it has fulfilled its purpose in this world. Considering it nearly died while protecting you, you understand it has more than earned its early retirement from following adventurers on dangerous errands. Waving goodbye to your one-time defender, you make your way back to Denalan at Wellspring Hovel.

\progress{Oakenscowl}

You show Denalan the Gargantuan Tumor.

\complete{Oakenscowl}

The threat of the Timberlings finally dealt with, you make your way to Corithas who should be waiting for you at the crossroads near Darnassus by now.
