You approach General Hawthorne.

\custom{General Hawthorne}{Gossip Text}

\says{38018}{39041}  % What is your name, $c? $n? Welcome to the Barrens. You are standing at the vanguard of one of our most important operations on this continent. I would be honored if you were to lend us your strength.

\you{39123}  % Tell me what happened at Taurajo.

\says{38018}{39124}  % Ah yes, our assault on the Horde town of Taurajo. I struggled with the implications of the decision. Taurajo was admittedly what you might call a 'soft target,' primarily a hunters' camp. Still, it had been used to recruit, equip, and train Horde infantry for many years. When our scouts reported that Taurajo's most dangerous units were out on the hunt, we had to act quickly.

\you{39125}  % We sacked the town?

\says{38018}{39126}  % <Hawthorne wrinkles his brow.> I would prefer not to use the term 'sacked,' but yes, the attack went off flawlessly. We removed Taurajo from the equation, confiscated its arms, and destroyed its smithing facilities. The assault gave our forces considerable breathing room and knocked the enemy off balance. Nonetheless, during the assault, I instructed my men to leave a gap open in our lines...

\you{39127}  % Why did you do that?

\says{38018}{39128}  % Taurajo had a significant civilian population. I wanted to ensure that they could escape the fighting, and many did, finding refuge in the north. There are some, even in Alliance High Command, who argued that I let an opportunity slip away. That I should've taken hostages. But I don't see the value in those sort of terror-tactics. Hear me out, $n: I want this war to end someday. It won't ever stop if we butcher or imprison civilians. I just pray that there are those on the other side who see things as I do.

\startID{25043}  % Fields of Blood

\startID{25045}  % A Line in the Dirt

\completeID{25045}  % A Line in the Dirt

As you make your way out of the camp and into the plains, the cook comes at you.

\start{Lion's Pride}

You make your way through the plain, until you reach a small hill where are you place an Alliance banner. A few Alliance Dield Defenders rush to your position and start building walls to defend the hill.  Unfortunately, the banner has not gone unnoticed by the Horde either, as multiple Desolation Grunts attack the hill. They try to burn the banner but you and the defenders are able to keep control of the hill and kill the attackers.

Success! The hill is yours!

As you march further into the plains towards the Quillboar territory,  you are attacked by Plains Pridemane lions. As you manage to kill the beasts, you are ambushed by Desolation Grunts. Exhausted from your fight with the lions,  you are not sure you will be able to overcome your attackers. Hopefully, a Northwatch Recon patrol rushes in to help you. You kill the grunts with the help of the Northwatch Recons, and thank the soldiers as you continue your way to the Quillboar's dwellings.

You enter the Bristleboar challenge ring and uses the Horn of Challenge to challenge Sabersnout to single combat.

A huge armored quillboar enters the ring.

\says{37513}{37125}  % What is this? <Gurgle> <Snort> The $r has come? To challenge mighty Sabersnout <Snort>?

Its entire clan is standing in circle around the two of you.

\says{37513}{37126}  % I will make example of $r <Snort>! Prepare yourself <Gurgle> soft-for-face.

The quillboar charges at you and the crowd cheers as the fight goes on. You gain the upper hand as Sabersnout starts hiding behind his shield.

\says{37513}{37128}  % You, <Snort> you are strong <Gurgle>. But...
\says{37513}{37129}  % Strong enough for THE BOARPOCALYPSE?

From all around you, you can see Bristleback Assault Boars rushing in the challenge ring to attack you.  You are outnumbered but manage to kill the boars regardless.

\says{37513}{37130}  % You ... survive the boars? <Snort> So many boars! So sad! <Gurgle>

Sabersnout, now enraged, lowers his shield and charges at you. You deflect the strike and kill him.

\says{37513}{37131}  % <Snort>? <Gurgle>!

His entire clan run out of the ring, fleeing in fear.

The deed done, you return back to the camp.
