\textit{In years past, the Zandalar tribe, encompassing the wise and scholarly progenitors of the trolls, heroically assisted the Horde and the Alliance with thwarting the nefarious activities of their brethren in Zul'Gurub and Zul'Drak. Yet the chaos unleashed by the recent Cataclysm has reshaped the Zandalari's philosophy about the world and the dwindling remnants of their race. Led by a mysterious prophet known only as Zul, the Zandalari have issued a call to Azeroth's embattled troll populations: unite into a single mighty empire and save their race from extinction).}

% Source: https://worldofwarcraft.com/en-us/news/2514161/patch-4-1-content-preview-rise-of-the-zandalari

\begin{center}
  $\ast$~$\ast$~$\ast$
\end{center}

Zul says: Our kind faces extinction. Trolls once ruled the mightiest empire this world has ever seen. Yet look at you now. Zul'drak has already fallen to the Scourge. Its gods consumed as death descended on its people. Zul'Farrak! Once the shining jewel of Tanaris is now nothing but a wasteland.

Zul says: Divided you are weak, but we Zandalari can offer you a future undreamed of. Jin'do of the Gurubashi, would you see the greatness of Zul'Gurub restored? Join us and the Zandalari will make it so. Daakara of the Amani, summon your followers to Zul'Aman. Together, we will make Zul'jin's murderers weep for mercy. Brothers, hear us now! We Zandalari have returned to reclaim the former glory of our people. To see trolls retake the lands that are rightfully ours! And to crush any foolish enough to stand in our way. From the wreckage of the Cataclysm, the troll empire will rise again!

The troll leaders cheer at Zul with the exception of Vol'jin, who walks away.

Zul says: Vol'jin of the Darkspear, you would turn your back on your own people?

Vol'jin says: Da Horde is my people. If it be war you bring, then I stand against you.

Vol'jin leaves the gathering.

So be it, Darkspear! But against the powers we will soon unleash, none shall stand for long.

An image of Hakkar appears and roars.

\begin{center}
  $\ast$~$\ast$~$\ast$
\end{center}

% Yet Vol'jin and his Darkspear trolls are not aligned with the Zandalari. They have sworn to stand with their Horde comrades -- and even work with the Alliance -- should the trolls ignite a new war on Azeroth. Soon, Vol'jin might be forced to act on his promise, for if the Gurubashi and Amani are left to their own devices, the world will know the legendary strength and savagery of the ancient troll empires once again.
% https://worldofwarcraft.com/en-us/news/2657805/patch-4-1-rise-of-the-zandalari-trailer-revealed

% In years past, the Zandalar tribe, encompassing the wise and scholarly progenitors of the trolls, heroically assisted the Horde and the Alliance with thwarting the nefarious activities of their brethren in Zul'Gurub and Zul'Drak. Yet the chaos unleashed by the recent Cataclysm has reshaped the Zandalari's philosophy about the world and the dwindling remnants of their race. Led by a mysterious prophet known only as Zul, the Zandalari have issued a call to Azeroth's embattled troll populations: unite into a single mighty empire and save their race from extinction.
% Thus far, the Gurubashi and Amani trolls have answered the summons and received aid from the Zandalari, allowing them to rebuild their respective capitals in Zul'Gurub and Zul'Aman. Not all trolls, however, have so eagerly adopted the Zandalari's grandiose vision of a new troll empire. Vol'jin and his Darkspear tribe are opposed to the warmongering espoused by Zul. To prevent the burgeoning Gurubashi and Amani troll forces from wreaking havoc on Azeroth, Vol'jin has reached out to his Horde comrades and members of the Alliance for assistance. Should the Darkspears' campaign fail, a new troll empire shall rise and bring war to a world already beset by suffering and conflict.
% https://worldofwarcraft.com/en-us/news/2514161/patch-4-1-content-preview-rise-of-the-zandalari
