Behind you arrives a sentinel mounted on a white hippogryph.

\miss{Lor'danel Sentinel says: Priestesses, I am to bring word that there are more survivors incoming. They are doing everything they can to sift through for the ones that are still alive, please send any help that you can!}

\miss{Dentaria Silverglade says: Understood, Sentinel. Return to the beach and aid them in bringing back any that are still alive.}

\miss{Lor'danel Sentinel says: Of course, Priestess.}

\start{The Last Wave of Survivors}

Making your way to the shore, a Ranger accosts you as you cross the western bridge.

\miss{You there! We need able bodies as fast as possible. Lives depend on it!}

\start{Threat from the Water}

Arriving at Mist's Edge, you notice the shoreline is dotted with Vile Spray, small water elementals. You spot multiple Lor'danel Sentinels trying to take down a gigantic water elemental. Lending a hand to the defenders, you help them kill this Vile Terror. Upon death however, it splits into more smaller Vile Sprays. Considering the Sentinels will be able to handle the smaller ones, you continue your way on the shore in search for survivors. You notice Sentinels mounted on hippogryph in the sky, as they are making round trips to Lor'danel from the shore to rescue survivors.

Further on, you notice another group of sentinels who are actively trying to push back Vile Sprays to the water. Spotting a body along the shore, you run to it.

\miss{Volcor's body lies motionless. As you begin to move away, a hand reaches out and grabs your ankle. He's alive!}

Signaling to the sentinels, one of them mounted on a nightsaber comes your way.

\miss{Lor'danel Sentinel says: Volcor... I'm so glad to see that you made it. But where is Grimclaw ?}

\miss{Lor'danel Sentinel says: We'll worry about him later. I need to get you to safety.}

\miss{Lor'danel Sentinel says: Thank you for your help, friend. I'll take it from here.}

As the mounted sentinel takes care of Volcor, you approach another sentinel who is kneeling next to a body.

\miss{Dalmond's body looks almost peaceful, buried only in the sand.}

As the kneeling sentinel does not adress your presence at all, you suspect she might have known Dalmond very well and is grieving from the loss. Not wanting to intervene in her mourning, you continue your search for suvivors, as you spot a body on a rocky "monticule" a few yards into the water.

\miss{Gershala Nightwhisper rolls onto his side to look at you as you approach and you see a hopeful smile creep onto his face.}

The Sentinel on the shore, realizing you found someone that can still be saved, swims to your position to help you.

\miss{Lor'danel Sentinel says: Gershala... Dentaria will be so happy to see you alive.}

Suddenly, she takes on her bow and begins shooting arrows in direction of the sea when you realize Vile Sprays have noticed the three of you and are closing in. You help the Sentinel killing the approaching Vile Sprays and together successfully defend Gershala.

\miss{Lor'danel Sentinel says: I'll take him back to the priestess. Thank you for your kindness.}

As you return on Mist's Edge searching for survivors, you notice a body at the edge of the beach near the woods.

\miss{As you approach, you hear Cerellean Whiteclaw gasp for breath. He looks to stand a chance if rescued soon.}

You signal him to a nearby sentinel on the beach.

\miss{Lor'danel Sentinel says: Cerellean! You made it!}

\miss{Lor'danel Sentinel says: I'll get him back to Lor'danel. Thank you for your help, stranger.}

You run to another body on the beach and kneel next to it.

\miss{The night elf turns to you as you approach and reaches for your hand.}

\miss{Gwennyth Bly'Leggonde says: It is too late for me. We earned our fate with our pride. Go... others may have made it. Save any that you can.}

\miss{Her grip loosens as life slips from her.}

Spoting a body floating in the water, you swim to it, fighting your way throuh the Vile Sprays, hoping it is not too late for this one as well.

\miss{Allyndia's body bobs gently in the surf. It appears that she's been dead for some time.}

Returning to the shore, you run to yet another body in the sand.

\miss{Terenthis' eyes stare unblinking into the distance, betraying the sorrow of hist last moments.}

You hope it is not too late as well for the two other bodies you can spot from here. As you approach the first one, her face turns to you.

\miss{Mavralyn says: So this... is what it feels like... to be mortal ?}

\miss{The question trails off as Mavralyn's breating stops.}

You run to the last body on the shore.

\miss{A whisper escapes Shaldyn's throat as you approach.}

\miss{Shaldyn says: Help... please.}

You wave to the flying sentinel on hippogryph to help you rescue her.

\miss{Lor'danel Sentinel says: Shaldyn!}

\miss{Lor'danel Sentinel says: I will see to it that Shaldyn is returned safely. Thank you, hero.}

Fighting your way back to Lor'danel through the Vile Sprays still assaulting the beach, you notice a new Vile Terror as risen from the depths. You help the Sentinels kill this one as well, and Ranger Glynda Nal'Shea notices the fight from Lor'danel western bridge. She addresses you when you return to town.

\complete{Threat from the Water}

Nodding to the ranger, you make your way back to Dentaria.

\complete{The Last Wave of Survivors}

The other priestess, still inspecting Laird's dead body, addresses you.

\start{The Boon of the Seas}

\miss{Serendia Oakwhisper says: When the wounded arrive, we will be putting them up in the Inn while we tend to their recovery. Please find us there when you return.}

As you head to the beach, a gnome followed by a night elf adresses you.

\start{Buzzbox 413}

% TODO: Johnathan Staats' fishing quest.

Diving in the water below Lor'danel, you find Encrasted Clams and remove their muscle, hoping it will be enough to save the survivors. You dive further in the sea in search for Corrupted Tide Crawlers. When you found a few of them, you realize your are running out of breath, and quickly make your way to the closes shoreline, on the east. You notice a strange mechanical box on the shore, this is probably the Buzzbox.

\progress{Buzzbox 413}

You put the Corrupted Tide Crawler Flesh into the machine.

\complete{Buzzbox 413}

\start{No Accounting for Taste}

Searching around the beach, you notice a Decomposing Thistle Bear with a Corrupted Tide Crawler eating from it. You take a Foul Bear Carcass Sample and make your way back to Lor'danel to deliver the Encrusted Clam Muscles to Serendia in the Inn.

\progress{The Boon of the Seas}

You hand her the clam muscles.

\complete{The Boon of the Seas}

You exit the Inn as Wizbang notices you.

\progress{No Accounting for Taste}

You give him the Foul Bear Carcass Sample.

\complete{No Accounting for Taste}

\start{Buzzbox 723}

You make your way south of Lor'danel by taking the long bridge accross the huge flooded cracks in the ground. You still can't believe the water in the cracks is flooding inwards into the continent rather than the opposite.

Entering the woods of Darkshore, you realize the leaves on the trees are showing unhealthy dark hues and the grass looks so sick that, would you have to choose a color to describe it, you might choose \emph{dark gray}. It looks like nature is clinging to this land despite it getting more and more corrupted over time.

As you venture into the woods, you are attacked by Corrupted Thistle Bears. Surprisingly enough, some kind of rat is attacking the bears at the same time. You kill the thistle bears as the rat run away from their corpses and you take the bear guts for the Buzzbox. As you near the box, you are attacked by a Corrupted Thistle Bear Matriarch. You would rather not kill her in front of the Thistle Bear Cubs, but the matriarch clearly has no intention of backing down and let you live another day. You frighten the cubs away so that they won't have to watch and you save your life from the Corrupted Thistle Bear Matriarch.

Hoping to find the source of this corruption so that the cubs can grow uncorrupted, you approach the Buzzbox.

\progress{Buzzbox 723}

You put the Corrupted Thistle Bear Guts into the machine.

\complete{Buzzbox 723}

\start{A Cure In The Dark}

Looking around you, you notice the waterfall. The path to it lies more to the west though, as the Cataclysm that created the cracks in the ground has also created stiff cliffs around this place. You find the path that leads to the cave thanks to Corrupted Duskrat running the ramp down into the woods. As you ascend the path to the waterfall, you notice empty cages along the way. Near the top of the path, you see Tharnariun, the night elf companion of the gnome, who seem to be retaking his breath after a long run.

\start{The Corruption's Source}

You advance to the waterfall when you notice Vile Grells are guarding it. You kill the foul creatures and enter Cliffspring Hollow, the cave hidden behind the waterfall.

The cave is swarming with more Vile Grells as well as Vile Corruptor satyrs. As you fight your way in the lowly illuminated corridorsof the cave, you find samples of Foul Ichor on the dead demons bodies. This is possibly what have been corrupting the wildlife in Duskwood. One of the demons was even in possession of a Corruptor's Master Key however.

\start{Bearer of Good Fortune}

You follow the ramp further down into the cave when you encounter a blue-skinned imp\rare{Licillin} who looks like he is currently corrupting a nearby animal in a cage. You kill the demon and start running everywhere in the cave while freeing the still uncorrupted animals you can find. One of the recesses of the cave is containing a lot of cages, and is there that you find Zenn Foulhoof, the mastermind behind the corruption of Darkshore's wildlife. You attack the satyr, and mercilessly kill him as he tries to flee from the fight. You free the animals from the cages around you and continue exploring the cave in search of more cages.

Continuing to explore the cave, you end up in a remote another part of it where you notice a Forsaken apothecary making some kind of experiments. This clearly can't be for any good.

\miss{Apothecary Furrow mutters to himself in Forsaken.}

You assault the Forsaken as his personal imp, Greef, comes in from a corner to defend him. Killing both of them, you look closer to the experiments he was working on.

\start{A Troubling Prescription}

As you smash the apothecary's workbench, the mixed chemicals spew everywhere as the bench itself starts to burn in obnoxious blue fumes. Freeing the last animals you can find in the cave, you return to the entrance.

As you exit the cave through the waterfall, you realize the water you can see from the cliff is flowing towards the sea, which means this water and the one that flows inwards from the shore must be converging somewhere.

Descending down the path and following along the river, you end up in front of a giant whirlpool that, all of the water of Darkshore, including the one from the sea, seems to drain into.

\ask{Jump into the whirlpool ?}
\goto{Maw of the Void}

You figure that Darkshore must be riddled with huge underground caves to be able to swallow so much water for so long. You suppose that, at some point, when the undergrounds of Darkshore are completely filled, this crevice's water level will rise such that the water starts flowing back into the sea again as it is meant to be.

You make your way back to Lor'danel to let Wizbang know of your discovery about the corruption of the duskrats.
