Jumping into the whirlpool, the current sends your body spiraling to the center of the water, where you are inevitably sucked below the waterline.

You end up following the water as it falls in the Bashal'Aran Collapse, a huge underground ruins complex which is being gradually filled with the waters of Darkshore. You drop into the water filling the bottom of the ruins and make your way out of it.

Near the water is a kneeling night elf druid.

\miss{Bielara Ivyshroud says: I wasn't expecting anyone down here. Come to keep me company, or just looking for a way out ?}

Not wanting to leave before having explored the few parts of the collapse that have not been submerged yet, you refuse the elf's offer. However, she does not seem to be interested in exploring the ruins at all, as she stays there, staring at the water, while you continue on.

As you explore the ruins, you take a ramp up, where you are attacked by two highborne spirits.

\miss{Forlorn Highborne says: Your life has no purpose.}

\miss{Forlorn Highborne says: Join us... forever.}

\miss{Forlorn Highborne says: The cold comes...}

The spirits defeated, you continue your way up the ramp, which circles around the ruins and the underground waterfall coming from the whirlpool above.

At the top of the ramp is another kneeling night elf, except this one is not a druid. He is surrounded by candles and jars, and you notice some of the jars have been smashed. As you approach him, he draws his glaives and attacks you.

\miss{Telarius Voidstrider says: You are not of the dark path! You do not belong here, adventurer!}  % <race>

As you fend off the night elf attacks and manage to injure him still, he draws on all his power and transforms into a demonic perversion of himself, with wings, horns and hooves. A blue aura emannates from his body, which is now twice its original size.

\miss{Telarius Voidstrider says: The shadows will consume you. You are not prepared to face the void.}

Making your stand against the demon, you manage to defeat him. On his corpse, you find the Writings of the Dark Herald.

\start{Writings of the Void}

You continue to explore the few parts of the ruins that are still accessible and are worried to realize that there is no way out of the collapse. You remember the night elf below offered you a way out. You make your way back to the waterline, and return to Bielara Ivyshroud.

\miss{You say: I'd like to leave this place.}

Without offering any word of reply, Bielara suddenly teleports you into a small cave out of the collapse. You can see the sky and the sick trees of Darkshore from the entrance a few yards away.

You wonder if Bielara knew there was a demon hunter hiding in the ruins. She seemed completely oblivious to anything that was happening around her, simply staring at the waterline. You realize she must have been sent there to rescue the ones carried away by the waters into the whirlpool, and that the loneliness of her task may have gotten at her. For her sake, you wish the collapse will soon be completely filled with water so that she can be freed from her duty.

You make your way back to Lor'danel to give the Writings of the Dark Herald to Ranger Glynda Nal'Shea.

As you approach her, she notices you.

\miss{Ranger Glynda Nal'Shea says: How can I help you, adventurer?}  % <class>

You show her the scrolls and tell her these etched writings reveal certain secrets on the path to becoming a Demon Hunter.

\complete{Writings of the Void}

Glad that jumping into a giant whirlpool actully served a purpose, you suddenly remember your initial task about the corruption of the duskrats. You run to Wizbang to let him know of your discovery from Cliffspring Hollow.
