As you approach Wizbang and Tharnarium, the gnome notices you.

\progress{A Cure In The Dark}

You give him the Foul Ichor that you found on the demons as you recount to the two of them what you saw in the cave and how you killed Zenn Foulhoof.

\complete{A Cure In The Dark}

\complete{The Corruption's Source}

\complete{Bearer of Good Fortune}

Continuing your story, you mention the apothecary and take Apothercary Furrow's Notes out of your bag.

\progress{A Troubling Prescription}

You hand the notes to Tharnarium.
% TODO: read Apothecary Furrow's Notes
% TODO: Tharnarium quote somewhere !

\complete{A Troubling Prescription}

As Serendia waves at you from the Inn, you make your way to the survivors that you rescued.  % TODO: remember, she said something like "yeah come back later for the survivors"

You approach Cerellean who is staring at the see.

\start{A Love Eternal}

Nodding to Cerellean, you hear Volcor "gémir" from his bed besides you.
% TODO: Gershala is there, does he say something ?

\start{A Lost Companion}

As you exit the inn, Ranger Glynda addresses you.

\start{The Final Flame of Bashal'Aran}
\progress{The Final Flame of Bashal'Aran}

\miss{Ranger Glynda Nal'Shea says: Be sure to stop by the bridges southeast of town. You should be able to secure a nightsaber to get you down the ruins.}

Following the advice, you take the bridge out of Lor'danel and approach the Nightsaber Rider at the other end of it.

\miss{You say: I'd like to travel to Bashal'Aran.}

She puts you on one of her nightsabers and instructs it to transport you to Bashal'Aran. The nightsaber follows the road south of Lor'danel until it approaches a ruined area. By the ramp into the ruins are two night elves. One one Nightsaber Rider and another who addresses you as you give the nightsabers reins to the rider.

\start{Solace for the Highborne}

Entering Bashal'Aran, you are greeted by Writhing Highbornes spirits who attack you on sight. You make your way through the ruins until you find The Final Flame of Bashal'Aran, a brazier bathed in an minous blue aura. As you extinguish the flame, you hear a Cursed Highborne yell in the distance, and more spirits coming to fight you.

\miss{Writhing Highborne says: "The cold comes..."}

You continue to fight your way into the ruins until you notice one spirit who is not attacking you. It mist be Anaya Dawnrunner, the decesed wife of Cerellean. Carrying the task he gave you, you attack the spirit and defeat it.

\miss{Anaya Dawnrunner says: Finally, my soul may rest... Oh, dearest Cerellean...}

On the ground where her spirit used to be, you find a pendant which was probably hers. You take it to give it to her husband.

You exit the ruins and return to Arya Automnlight near the entrace, telling her that the deed is done, and that the spirits of Bashal'Aran have been freed.

\complete{Solace for the Highborne}

Before taking your nightsaber back to Lor'danel, you decide to search for Grimclaw, Volcor's companion bear, who disappeared somewhere between the ruins of Auberdine and Lor'danel. On your way south, you notice the area has been damaged even more so than the north of Darkshore, as the road is completely broken by huge cracks in the ground, and some trees are leaning towards the ground as you notice a huge tornado a few miles forward.

From the top of the crack where you are standing, you spot a white bear on the floor to the right, with a Keeper of the Grove and a dryad beside him. You manage to descend in the crack then ascend the other side as you approach the pair and notice that Grimclaw lies injured on the ground.

\miss{Keeper Karithus says: Welcome, child.}

\complete{A Lost Companion}

\start{Unsavory Remedies}

\progress{Unsavory Remedies}  % TODO: poachers ?

\start{Twice Removed}

\start{Ritual Materials}

As you can spot Moonstalkers sleeping under some trees near you, you decide to start by gathering the materials for Karithus' ritual.

You approach the sleeping Moonstalkers and quietly pull out a few of hiw whiskers and start running away. \miss{The moonstalker rises, angry at being disturbed}, but you are already far enough that it does not understand what woke it. You spot another group of sleeping Moonstalkers nearby and approach them to take some of their whiskers as well. As you force some of the closes one's hair, \miss{the moonstalker wakes suddenly and lets out a low growl}, waking up the other one. \miss{The moonstalker jumps to its feet, teeth bared.} Surprised, you start to run away, the Moonstalker Whiskers in your hand.

After running a few yards away, the moonstalkers stop chasing you and return to their slumber under the trees. You realize you just entered the stags territory. Hiding behind one of the trees, you wait for the great stag to wander further away from the does. Once the way is clear, you slowly approach the does and pull off a Thuft of Mottled Doe Hair. The doe starts running toward the stag for protection. Fearing the stag's retribution, you jump into the nearby river and stay under water to hide from it.

A moment later, you stick your head out of the water to breathe and you spot some Hungry Thistle Bear trying to fish for salmons. One of them is eating nearby and does not notice you as you approach it from the water. You pull off a bit of the hair from its thick hide but the bear, its attention caught by its delicious meal, does not react at all.

Further along the inwards-flowing river, you notice a naga on a ridge. The serpentine humanoid seems to stand guard at the entrance of the Ruins of Lornesta. You quietly approach the ruins and you spot multiple nagas in the shallow waters. This is probably the Darkscale nagas that Seraphine wants you to kill. You engagne the Darkscale Scouts and benefit from the surprise element, allowing you to kill a few of them easily. Unfortunately, you miss one of them attempting to run away in fear. As he rallies other Darkscale Scouts, you use Seraphine's Petrified Root on the body of the fallen naga, which \miss{raises an Ent from the nourishing remains of a dead Darkscale Scout.}

The group of Darkscale Scouts rallied by the escaping one approaching you way, you charge at the nagas with the Withered Ents on your side. You realize one of the naga in the group is slimmer and has four arms, without a doubt \rare{Lady Vespira}a sorceress. You engage the sorceress as the Withered Ents attack the Scouts. The scouts are quickly dealt with, but the remaining naga casts a Forked Lightning which instantly kills the ents. Using the Petrified Root again, you raise new Withered Ents from the bodies of the scouts and overwhelm the sorceress.

As you start to harvest some of the Fuming Toadstool mushrooms around the ruins for Karithus, you are attacked by yet another group of nagas. These ones are not merely supported by a sorceress, they are lead by her.

\miss{Lady Janira says: We will suffer no interruptions!}
\miss{Lady Janira says: The age of the night elves is coming to a close.}
\miss{Lady Janira says: You live on borrowed time. The sea will consume you.}
\miss{Lady Janira says: Queen Azshara will return and your land will be forfeit.}

Giving all you got, you manage to kill a few Darkscale Scouts and raise some more Withered Ents. With their help, you manage to overthrow Lady Janira. As the ents start running amock killing the remaining nagas fleeing, you harvest a few Fuming Toadstoll.

You make your way back to Keeper Karithus and Seraphine and start retelling the fight you just went through.

\complete{Twice Removed}

You hand the mushrooms to Karithus.

\complete{Unsavory Remedies}

\progress{Ritual Materials}

You hand the materials to Karithus.

\complete{Ritual Materials}

Karithus mixes the material and puts a bowl with the resulting incense on the ground, between you, him, and Grimclaw.

\start{The Ritual Bond}

\progress{The Ritual Bond}

You \miss{breathe in the smoke to entice visions of the great animal spirits.}

You are \miss{immersed in a deep trance}. The surrounding woods appear blurry, and you can't see Grimclaw or Seraphine anymore, only you and Karithus remain. Looking around you, you realize the woods are empty of all creatures, save three animal spirits.

You approach the Great Thistle Bear Spirit.

\start{Spirit of the Thistle Bear}

You decide to hear all the spirits before making your choice. You bow at the bear, then approach the Great Moonstalker Spirit.

\start{Spirit of the Moonstalker}

You nod to the moonstalker and approach the Great Stag Spirit.

\start{Spirit of the Stag}

You choose one of the three animal spirits to receive its blessing then return to Karithus.

\complete{The Ritual Bond}

As Karithus proceeds to the Ritual Bond and you are \miss{undergoing the binding}, you can feel the Grovekeeper's Trance lifting from your mind as Karithus and Seraphine channels the powers of nature into you.

\miss{Keeper Karithus says: It is done. The spirit is bound with you and you will carry it with you anytime you are in Darkshore. May you serve nature well.}

\ask{Which animal spirit did you choose ?}
\goto[Blessing of the Thistle Bear]{} You are blessed by the Great Thistle Bear Spirit. Its resilience makes you stronger, and you are regarded in a friendly manner by the bears of Darkshore.
\goto[Blessing of the Moonstalker]{} You are blessed by the Great Moonstalker Spirit. Its ferocity makes you fight better, and you are regarded in a friendly manner by the moonwalkers of Darkshore.
\goto[Blessing of the Stag]{} You are blessed by the Great Stag Spirit. Its swiftness makes you move faster, and you are regarded in a friendly manner by the stag of Darkshore.

\start{Grimclaw's Return}

In order to race after Grimclaw, you return near the ruins of Bashal'Aran to take a nightsaber ride back to Lor'danel.

\miss{Nightsaber Rider says: I'm glad to see that you're well.}
\miss{Nightsaber Rider says: Looking for a ride?}

You mount the nightsaber as it quickly runs to Lor'danel. Once in town, you give the nightsaber back to the rider in Lor'danel and run to Ranger Glynda to tell her that the final flame of Bashal'Aran has been extinguised.

\complete{The Final Flame of Bashal'Aran}

You make your way up the Inn to Cerellean and give him Anaya's Pendant.

\progress{A Love Eternal}
\complete{A Love Eternal}

Near Cerellean is Grimclaw, despereately trying to wake Volcor from his bed. A priestess walks down from the upper level of the inn.

\complete{Grimclaw's Return}

She walks back upstairs as you exit the inn. A dwarf waves at you from below a night elf hut.

\start{An Ocean Not So Deep}

You swim into the sea in direction of the wreckage until you reach a small island with a gnome on it, this must be Gary. He is standing near a small robot and a control console.

\progress{An Ocean Not So Deep}

You approach the decoy boat control console and start controlling the robot which passes for foolhardy adventurer to the murlocs. The robot walks among the murlocs and attract some of them, starting to attack it.

You activate the robot's Depth Charge Countdown Pulse.

\miss{Foolhardy Adventurer says: Murloc pests, I have come to steal your treasure! Attempt to stop me! Quickly!}

More murlocs from all around the wreckage rush towards the Foolhardy Adventurer decoy robot.

\miss{Foolhardy Adventurer says:  Detonation imminent.}

The decoy robot exploses, killing all the murlocs.

You make your way back to Lor'danel and the dwarf.

\miss{Gorbold Steelhand says: A treasure hunter's life is a treacherous one. Don't be foolin' yerself.}

\complete{An Ocean Not So Deep}

Ranger Glynda comes at you.

\start{The Shatterspear Invaders}

\miss{Ranger Glynda Nal'Shea says: Don't forget to check near the bridges southeast of town for a ride up to our forward post.}

You exit the town by the huge bridge across the flooded cracks in the ground and meet with the nightsaber rider

\miss{Nightsaber Rider says: Looking for a ride?}

\miss{You say: I'd like to travel to the ruins of Mathystra.}

She puts you on a nightsaber which starts running to the east. You pass near the tower of Althalaxx. It is in ruins and the trees around it are on fire. Along the way, you notice multiple Shatterspear Raiders corpses.

You reach the Ruins of Mathystra, where a small force of sentinels have set up camp. A few of them are inspecting a troll body. As you approach them, their leader turns to you

\complete{The Shatterspear Invaders}

\start{Shatterspear Laborers}

\start{Remnants of the Highborne}

You venture into the ruins, searching for relics. You kill the Shatterspear Laborers who are digging the ruins and save some Highborne Relics from the trolls. Further into the ruins, you are attacked by one of the Shatterpsear Overseers.

\miss{Shatterspear Overseer says: I be movin' to the groove; ya be movin' to the grave}

As you rummage through the body of the overseer, you find some papers.

\start{Reason To Worry}

You return back to the Sentinels' camp.

\progress{Reason To Worry}

You hand the Overseer's Orders to the Lieutenant.

\complete{Reason To Worry}

\complete{Shatterspear Laborers}

\progress{Remnants of the Highborne}

You give the Highborne Relics to Balthule.

\complete{Remnants of the Highborne}

\start{Swift Response}

\start{Denying Manpower}

\start{War Supplies}

You venture into the ruins again in direction of the Shatterspear trolls camp. As you approach the camp, you are attacked by a Tauren who seem to be guarding the entrance. You are attacked by more Horde Enforcers on your way into the camp but manage to defeat them.

Inside the camp you find Shatterspear Armaments stored inside crates marked with the symbol of the Horde. You use the Sentinel Torch to burn the crates.

The fire from the burning alerts the Shatterspear Mystics and other Horde Enforcers also run to your position. You manage to escape being slaughtered by hiding nearby, at the western end of the Shatterspear camp, where you realize the trolls even built some docks for ships.

Once the rumble is over, you make your way to the back of the camp where you notice a night elf body lying on the ground. You kill the Shatterspear Shamans along the way and kneel near the body.

\progress{Swift Response}

\complete{Swift Response}

\start{One Bitter Wish}

You engage Rit'ko, the Shatterspear Torturer.

\miss{Rit'ko says: A new victim! Me was almost don wit dis one anyway.}

Killing the torturer, you find a key on his dead body. You use the Shatterspear Torturere's Cage Key on a nearby cage.

\start{Timely Arrival}

You make your way back to the docks, killing the Enforcers and Shamans who have just found the bodies of their fallen comrades on the way and run to the end of the docks.

\miss{Sentinel Aynasha says: Thanks for getting me out of there. I should be able to swim back from here, but before I go, one quick thing... I was afforded a brief chance to attack their leader, and he was protected by some kind of magic. Make sure Morra hears of this before leading any kind of attack. Farewell newcomer. May Elune's blessing be with you.}

You take the time to burn a few more Shatterspear Armaments crates then jump into the water before the fire bring in more reinforcements again.

You swim back to the nearest shore, where you are attacked by Greymist Tidehunter murlocs. They are pale grey and purple in color, but they seem to be lead by a \rare{Flagglemurk the Cruel}smaller murloc which actually is a colorful one. Dispatching the murlocs, you make your way back to the Ruins of Mathystra.
